\Title

### 2022-09-14 Grimaldi-etal-BiolCybernetics.tex
model

\subsection{Hetero-synaptic delays model as a temporal Logistic Regression}
%
\begin{figure*}[ht!]
    {\centering
    \vspace{-3cm}
    \includegraphics[width=\linewidth]{figures/3D_kernels_oneline.png}
    }
    %\vspace{-.5cm}
    \caption{
    	Representation of the weights for the $8$ learned kernels of the model corresponding to the OFF polarities and selective to the different motion directions
	(because of the symmetry observed between the ON and OFF event streams, kernels are similar for the ON polarities). These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes.
	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. One sees positive (excitatory) coefficients for the specific direction of motion and negative (inhibitory) coefficients for all other directions.
	}
    \label{fig:kernels}
\end{figure*} 
%
The sensory signal representing the output of an event-based camera forms a discrete stream of events, which can be formalized as an ordered set of addresses and timestamps: $\event = \{(\presynaddr_\arank, \timev_\arank)\}_{\arank \in [1,\numevent]}$ where $\numevent \in \mathbb{N} $ is the total number of events in the data stream and the rank $\arank$ is the index of each event $\event_\arank$. 
This event has a time of occurrence $\timev_\arank$  and an associated address, which is typically in the form $\presynaddr_\arank=(x_\arank, y_\arank, \polev_\arank)$.
This defines a presynaptic address space $\presynaddrspace = [1, \Nx]\times[1, \Ny] \times [1, \Npol] \subset \mathbb{N}^3$ where $(\Nx, \Ny)$ is the size of the sensor in pixels and $\Npol$ is the number of polarities  ($\Npol=2$ for ON and OFF polarities).

@@

The corresponding input presynaptic spikes $\event$ will be integrated by this synaptic set and notably by the respective delays, which will multiplex in time all possible patterns.
For each time $\timev$ the integration of $\event$ is defined by a list of weights $\activeweights^\postsynaddr$ linked to the synapses that match a precise spatio-temporal motif as input:
$
toto
%\activeweights^\postsynaddr(t) = \{\synapticweight_\ranksyn^\postsynaddr | \presynaddr_\arank = \presynaddr_\ranksyn^\postsynaddr \; \text{and} \; \timev=\timev_\arank + \synapticdelay_\ranksyn^\postsynaddr\}_{\arank \in [1,\numevent]\text{, }\ranksyn \in [1,\Nsyn^\postsynaddr]}
$.
The activation function of our spiking neuron is a softmax function implementing a form of  Multinomial Logistic Regression (MLR)~\citep{grimaldi_robust_2022}, in analogy to a spiking Winner-Take-All network~\citep{nessler_bayesian_2013}. It transforms this list of weights into a probability with the following formula:
$
toto
%Pr(k=\postsynaddr \; | \; \timev) =
\frac 1 Z
{\exp  (\mathcal{C}^\postsynaddr(\timev) +\bias^\postsynaddr) }
$ 
where $\mathcal{C}^\postsynaddr(\timev) = \sum
\activeweights^\postsynaddr(t)
$ is the sum of the synaptic weights and $\bias^\postsynaddr$ is the bias linked to neuron $\postsynaddr$. 
In particular, we expect that some specific motifs may become tightly synchronized as they reach the basal dendritic tree, leading to a high postsynaptic activity which makes it progressively more likely to generate an output spike.
\subsection{A Spiking Neural Network detecting motion as a CNN}

@@

@@

>>>>

\subsection{Hetero-synaptic delays model as a temporal Logistic Regression}
The sensory signal representing the output of an event-based camera forms a discrete stream of events, which can be formalized as an ordered set of addresses and timestamps: $\event = \{(\presynaddr_\arank, \timev_\arank)\}_{\arank \in [1,\numevent]}$ where $\numevent \in \mathbb{N} $ is the total number of events in the data stream and the rank $\arank$ is the index of each event $\event_\arank$. 
This event has a time of occurrence $\timev_\arank$  and an associated address, which is typically in the form $\presynaddr_\arank=(x_\arank, y_\arank, \polev_\arank)$.
This defines a presynaptic address space $\presynaddrspace = [1, \Nx]\times[1, \Ny] \times [1, \Npol] \subset \mathbb{N}^3$ where $(\Nx, \Ny)$ is the size of the sensor in pixels and $\Npol$ is the number of polarities  ($\Npol=2$ for ON and OFF polarities).

@@

The corresponding input presynaptic spikes $\event$ will be integrated by this synaptic set and notably by the respective delays, which will multiplex in time all possible patterns.
For each time $\timev$ the integration of $\event$ is defined by a list of weights $\activeweights^\postsynaddr$ linked to the synapses that match a precise spatio-temporal motif as input:
$
toto
%\activeweights^\postsynaddr(t) = \{\synapticweight_\ranksyn^\postsynaddr | \presynaddr_\arank = \presynaddr_\ranksyn^\postsynaddr \; \text{and} \; \timev=\timev_\arank + \synapticdelay_\ranksyn^\postsynaddr\}_{\arank \in [1,\numevent]\text{, }\ranksyn \in [1,\Nsyn^\postsynaddr]}
$.
%
The activation function of our spiking neuron is a softmax function implementing a form of  Multinomial Logistic Regression (MLR)~\citep{grimaldi_robust_2022}, in analogy to a spiking Winner-Take-All network~\citep{nessler_bayesian_2013}. It transforms this list of weights into a probability with the following formula:
$
toto
%Pr(k=\postsynaddr \; | \; \timev) =
\frac 1 Z
{\exp  (\mathcal{C}^\postsynaddr(\timev) +\bias^\postsynaddr) }
$ 
where $\mathcal{C}^\postsynaddr(\timev) = \sum
\activeweights^\postsynaddr(t)
$ is the sum of the synaptic weights and $\bias^\postsynaddr$ is the bias linked to neuron $\postsynaddr$. 
In particular, we expect that some specific motifs may become tightly synchronized as they reach the basal dendritic tree, leading to a high postsynaptic activity which makes it progressively more likely to generate an output spike.
%

@@

\subsection{Extension as 3D convolutions for motion detection}

@@

\begin{figure*}[ht!]
    {\centering
    \vspace{-3cm}
    \includegraphics[width=\linewidth]{figures/3D_kernels_oneline.png}
    %\vspace{-.5cm}
    \caption{
    	Representation of the weights for the $8$ learned kernels of the model corresponding to the OFF polarities and selective to the different motion directions
	(because of the symmetry observed between the ON and OFF event streams, kernels are similar for the ON polarities). These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes.
	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. One sees positive (excitatory) coefficients for the specific direction of motion and negative (inhibitory) coefficients for all other directions.
    \label{fig:kernels}
\end{figure*} 
